A community-maintained standard library of population genetic simulations

### 2019-12-19 popSimManu.tex
a few more edits to Discussion

\documentclass[12pt,halfline,a4paper]{ouparticle}
\usepackage{amsmath,amssymb}
\usepackage[round]{natbib}
\usepackage{graphicx,rotating}
\usepackage{dsfont}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{siunitx}

@@

\affil[7]{Department of Human Genetics, McGill University}
\affil[8]{Melbourne Integrative Genomics, School of Mathematics and Statistics, University of Melbourne}
\affil[9]{Department of Mathematical Stochastics, University of Freiburg}
\affil[10]{Department of Genome Sciences, University of Washington}
\affil[11]{The Biodesign Institute and The School of Life Sciences, Arizona State University}
\affil[12]{Department of Human Genetics, David Geffen School of Medicine, University of California, Los Angeles}
\affil[13]{Department of Biology, Stanford University}
\affil[14]{Department of Ecology, Evolution, and Environmental Biology, Columbia University}
\affil[15]{Department of Computational Biology, Cornell University}
\affil[16]{Computer Technologies Laboratory, ITMO University}
\affil[17]{International Laboratory for Human Genome Research, National Autonomous University of Mexico}
\affil[18]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[19]{Big Data Institute, Li Ka Shing Centre for Health Information and
Discovery, University of Oxford}
\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\aleph$]{Denotes corresponding authors, listed alphabetically}
% JK: didn't bother with the \texttt stuff for stdpopsim in the abstract as it's nearly
% always dropped in production anyway.

@@

\renewcommand{\arraystretch}{1.2}
\begin{table}[t]
% Make sure the table is centered even though it's too wide
\makebox[\textwidth][c]{
    \begin{footnotesize}
    \input{model_table.tex}
    \end{footnotesize}
}
\caption{\label{tab:catalog}
Initial set of demographic models in the Catalog and simple benchmarks.
For each model we report the CPU time, maximum memory usage and the
size of the output \tskit file. In each case we simulate 100 samples
drawn from the first population, for the shortest chromosome of that species
and a constant chromosome-specific recombination rate.
The times reported are for a single replicate run on an Intel i5-7600 CPU.
These are not intended to be rigorous benchmarks, and the computing resources
required will vary widely depending on sample sizes, chromosome length,
recombination rates and other factors.
}
\end{table}

@@

\section*{Acknowledgements}
We thank the Probabilistic Modeling in Genomics conference organizers with making this collaboration possible.
Early on in the project we were helped by many people including XXXXXX.
CCK and KEL were funded under NIH Award R35GM119856.
JRA and ADK were funded under NIH Award R01GM117241.
TJS and RNG were funded under NIH award R01GM127348.
FR and GG were supported by a Villum Young Investigator award (project no.~00025300).
DODV is funded by a UC MEXUS-CONACYT Collaborative Grant and a DGAPA-PAPIIT grant (PAPIIT-IA200620).
JK is supported by the Robertson Foundation.

>>>>

\documentclass[12pt,halfline,a4paper]{ouparticle}
\usepackage{amsmath,amssymb}
\usepackage[round]{natbib}
\usepackage{graphicx,rotating}
\usepackage{dsfont}
\usepackage{xspace}

@@

\affil[7]{Department of Human Genetics, McGill University}
\affil[8]{Melbourne Integrative Genomics, School of Mathematics and Statistics, University of Melbourne}
\affil[9]{Department of Mathematical Stochastics, University of Freiburg}
\affil[10]{Department of Genome Sciences, University of Washington}
\affil[11]{The Biodesign Institute and The School of Life Sciences, Arizona State University}
\affil[12]{Department of Human Genetics, David Geffen School of Medicine, University of California, Los Angeles}
\affil[13]{Department of Biology, Stanford University}
\affil[14]{Department of Ecology, Evolution, and Environmental Biology, Columbia University}
\affil[15]{Department of Computational Biology, Cornell University}
\affil[16]{Computer Technologies Laboratory, ITMO University}
\affil[17]{International Laboratory for Human Genome Research, National Autonomous University of Mexico}
\affil[18]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[19]{Big Data Institute, Oxford Unviersity}
\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\aleph$]{Denotes corresponding authors, listed alphabetically}
% JK: didn't bother with the \texttt stuff for stdpopsim in the abstract as it's nearly
% always dropped in production anyway.

@@

\begin{table}[t]
\begin{footnotesize}
\input{model_table.tex}
\end{footnotesize}
\caption{\label{tab:catalog}
Details of the initial set of population models across four species.
\textbf{NOTES: Column names are ID, name (or description maybe?),
reference, CPU time, RAM}
}
\end{table}

@@

\section*{Acknowledgements}
We thank the Probabilistic Modeling in Genomics conference organizers with making this collaboration possible.
Early on in the project we were helped by many people including XXXXXX.
CCK and KEL were funded under NIH Award R35GM119856.
JRA and ADK were funded under NIH Award R01GM117241.
TJS and RNG were funded under NIH award R01GM127348.
FR and GG were supported by a Villum Young Investigator award (project no. 00025300).
DODV is funded by a UC MEXUS-CONACYT Collaborative Grant and a DGAPA-PAPIIT grant (PAPIIT-IA200620).
